---
title: "Trend Analysis"
author: "Christie Du"
date: "2/15/2022"
output: html_document
---

```{r}
packages.used = c("DT", "tidyverse", "zoo",
                  "pheatmap", "ggplot2", "dplyr",
                  "stringr")

packages.needed=setdiff(packages.used, 
                        intersect(installed.packages()[,1], 
                                  packages.used))

if(length(packages.needed)>0){
  install.packages(packages.needed, dependencies = TRUE)
}

library(DT)
library(tidyverse)
library(zoo)
library(pheatmap)
library(ggplot2)
library(dplyr)
library(stringr)

source("cleaning.R")
source("plots.R")
```

### Step 1: Load Data

```{r}
covid_calls = read.csv("../output/covid_calls.csv", na.strings=c("","N/A","NA"))
ncalls = read.csv("../output/ncalls_by_date_complaint.csv", na.strings=c("","N/A","NA"))
complaint_corr = read.csv("../output/complaint_corr.csv", na.strings=c("","N/A","NA"))
complaint_corr = complaint_corr %>%
  remove_rownames %>% column_to_rownames(var="X")%>%
  remove_rownames %>% column_to_rownames(var="term")
```


## Step 2: Covid-19 calls throughout the pandemic

Different Phases of the Pandemic:

1. Initial outbreak (Mar 2020 - Jun 2020)
2. Covid cases go down (Jun 2020 - Nov 2020)
3. Covid cases go up + Delta variant (Nov 2020 - Jun 2021)
4. Covid cases go down (Jun 2021 - Nov 2021)
5. Covid cases spike + Omicron variant (Nov 2021 - present)

### Barcharts of most common Covid-19 call types

```{r}
covid_complaints = unique(covid_calls$Complaint.Type)
```

```{r}
by_covid_complaint = process.freq.df(covid_calls)
datatable(by_covid_complaint)
# omit datatable for dashboard - simply for viewing
```

```{r}
plot.freq.bp(by_covid_complaint)
```

### Time Series of Covid Calls

```{r}
plot.ts.complaints(covid_calls)
```

# Viewing covid call volume by borough

```{r}
neighborhoods = read.csv("../data/nyc_zip_borough_neighborhoods_pop.csv", na.strings=c("","N/A","NA"))
borough_pop = neighborhoods %>% 
  group_by(borough) %>% 
  summarise(total_pop = sum(population))
```


```{r}
complaint = "noncompliance with phased reopening"
plot.borough.bp(covid_calls, complaint)
```

## Step 3: Correlation between Covid Calls and Non-Covid Calls

```{r}
colnames(complaint_corr) = c("non-compliance\nw/phased\nreopening",
                                  "vaccine mandate\nnon-compliance",
                                  "mass gathering\ncomplaint",
                                  "covid-19\nnon-essential\nconstruction",
                             "face covering\nviolation")
```


```{r}
plot.corr(complaint_corr)
```


```{r}
datatable(complaint_corr, 
          options = list(pageLength=5)) %>%
  formatRound(columns = colnames(complaint_corr), digits=3)
# add datatable to dashboard
```

```{r}
formatRound(complaint_corr, columns = colnames(complaint_corr), digits=3)
```


